---
title: "Industry decarbonization by 2050"
date: "27/11/2018"
---

This is a republication of a poster presented on 28 November 2018 in Brussels.

<center>
<blockquote class="twitter-tweet" data-lang="nl"><p lang="en" dir="ltr">A little more than a month ago I presented our <a href="https://twitter.com/REINVENT_EU?ref_src=twsrc%5Etfw">@REINVENT_EU</a> <a href="https://twitter.com/hashtag/scenario?src=hash&amp;ref_src=twsrc%5Etfw">#scenario</a> and <a href="https://twitter.com/hashtag/modelling?src=hash&amp;ref_src=twsrc%5Etfw">#modelling</a> work on <a href="https://twitter.com/hashtag/EU?src=hash&amp;ref_src=twsrc%5Etfw">#EU</a> <a href="https://twitter.com/hashtag/industry?src=hash&amp;ref_src=twsrc%5Etfw">#industry</a> <a href="https://twitter.com/hashtag/decarbonisation?src=hash&amp;ref_src=twsrc%5Etfw">#decarbonisation</a> by 2050 at the REINVENT stakeholder workshop in Brussels. Condensing our long read (<a href="https://t.co/1128YI0BBA">https://t.co/1128YI0BBA</a>) to a more appealing short read! <a href="https://t.co/7jjvuQanI4">pic.twitter.com/7jjvuQanI4</a></p>&mdash; Mariësse van Sluisveld (@marieyesse) <a href="https://twitter.com/marieyesse/status/1080817415959793664?ref_src=twsrc%5Etfw">3 januari 2019</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
</center>

## Integrated Perspective

[REINVENT](http://www.reinvent-project.eu)’s zero-order analysis utilises an **analytical framework** in which two quantitative models are used to independently provide long-term perspectives on EU industry **decarbonisation by 2050** via common indicators (CO~2~, energy use and production volume)

## Traditional Strategies dont add up 

Our study shows that today‘s available technologies and **BAT energy efficiency** options are **not** sufficient to reach full industry decarbonization.  All industries need novel low-carbon technologies, processes & materials. 


```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.align="center", fig.width=8, fig.height=4, fig.cap="_**Figure**: Expected and required change of decarbonisation, energy efficiency and sufficiency (in % change)_"}

library(plotly)
library(ggplot2)
library(data.table)
library(dplyr)
library(tidyr)


WISEECO2_0= read.csv("data/WISEE_CO2_emissions_22_6_2018.csv", sep=";", dec=",")
WISEECO2=melt(WISEECO2_0,  id.vars=c("Model", "Sector", "Variable","Scenario"), variable.name="Year")
WISEECO2$Year = as.numeric(as.character(substr(WISEECO2$Year, 2, stop=100)))
WISEECO2$value = as.numeric(WISEECO2$value)
#WISEECO2 <- na.omit(WISEECO2)
WISEECO2=data.table(WISEECO2)

WISEECO2=spread(WISEECO2, Year, value)
setnames(WISEECO2, "2015", "X2015")
setnames(WISEECO2, "2030", "X2030")
setnames(WISEECO2, "2050", "X2050")
WISEECO2 = WISEECO2 %>% mutate(RED2030=(1-(X2030/X2015))*100, RED2050=(1-(X2050/X2015))*100)
WISEECO2=data.table(WISEECO2)
WISEECO2=WISEECO2[Sector=="Chemical", Sector:=c("Chemicals and Petrochemicals")]

# IMAGE

ALLVAR=read.csv("data/Compilation_IMAGE_REINENT_everything.csv", sep=";", dec=".")
ALLVAR$value <- as.numeric(ALLVAR$value)
ALLVAR$Year <- as.numeric(ALLVAR$Year)
ALLVAR=data.table(ALLVAR)

CO2TAB= ALLVAR[ Variable %in% c(
                  "Emissions|CO2|Iron and Steel|Direct emissions",
                  "Emissions|CO2|Pulp and Paper|Direct emissions", 
                  "Emissions|CO2|Chemicals and Petrochemicals|Direct emissions",
                  "Emissions|CO2|Food Processing|Direct emissions"
                ) & Year %in% c("2015", "2030", "2050") & Region=="EU28"]
CO2TAB$Variable <- gsub("|Direct emissions", "", CO2TAB$Variable, fixed=T )

CO2TAB$Variable <- gsub("Emissions|CO2|", "", CO2TAB$Variable, fixed=T )
CO2TAB=spread(CO2TAB, Year, value)
setnames(CO2TAB, "2015", "X2015")
setnames(CO2TAB, "2030", "X2030")
setnames(CO2TAB, "2050", "X2050")
CO2TAB=CO2TAB %>% mutate(RED2050=(1-(X2050/X2015))*100, RED2030=(1-(X2030/X2015))*100)
setnames(CO2TAB, "Variable", "Sector")

CO2REDTAB = rbind(WISEECO2[Variable=="Emissions|CO2", c("Model","Sector", "Scenario", "RED2030", "RED2050")],CO2TAB[, c("Sector", "Scenario", "Model", "RED2030", "RED2050")] )
CO2REDTAB2=gather(CO2REDTAB, RED, value, c(RED2030, RED2050))

#write.table(file="datatables/overview_table_indicators_CO2RED.csv", CO2REDTAB2, sep=",", dec=".", row.names=FALSE)
CO2REDTAB2=rbind(CO2REDTAB2, data.table(Model=c("WISEE", "WISEE"),
                                                Sector=c("Food Processing","Food Processing"),
                                                Scenario=c("CIRC", "CCS"),
                                                RED=c("RED2030", "RED2050"),
                                                value=c(0,0)))
CO2REDTAB2=data.table(CO2REDTAB2)
CO2REDTABminmax=CO2REDTAB2[!Scenario=="Baseline",list(ymax=max(value,na.rm = TRUE),ymin=min(value,na.rm = TRUE)),by=c("Model","Sector", "RED")]
CO2REDTABminmax$Variable <- "CO2 Emissions"

## FINAL ENERGY REDUCTIONS
FINETABRED=ALLVAR[Variable %in% c("Final Energy|Industry|Pulp and Paper",
                                  "Final Energy|Industry|Iron and Steel",
                                  "Final Energy|Industry|Chemicals and Petrochemicals",
                                  "Final Energy|Industry|Food Processing"
) & Year %in% c("2015", "2030", "2050") & Region=="EU28"]
FINETABRED$Variable <- gsub("Final Energy|Industry|", "", FINETABRED$Variable, fixed=TRUE)
setnames(FINETABRED,"Variable", "Sector")
FINETABRED=spread(FINETABRED, Year, value)
setnames(FINETABRED, "2015", "X2015")
setnames(FINETABRED, "2030", "X2030")
setnames(FINETABRED, "2050", "X2050")
FINETABRED=FINETABRED %>% mutate(RED2050=(1-(X2050/X2015))*100, RED2030=(1-(X2030/X2015))*100)

FINEREDTAB = rbind(WISEECO2[Variable=="Final Energy", c("Model","Sector", "Scenario", "RED2030", "RED2050")],FINETABRED[, c("Sector", "Scenario", "Model", "RED2030", "RED2050")] )
FINEREDTAB2=gather(FINEREDTAB, RED, value, c(RED2030, RED2050))
FINEREDTAB2=data.table(FINEREDTAB2)
FINEREDTAB2=rbind(FINEREDTAB2, data.table(Model=c("WISEE", "WISEE"),
                                        Sector=c("Food Processing","Food Processing"),
                                        Scenario=c("CIRC", "CCS"),
                                        RED=c("RED2030", "RED2050"),
                                        value=c(0,0)))
FINEREDTABminmax=FINEREDTAB2[!Scenario=="Baseline",list(ymax=max(value,na.rm = TRUE),ymin=min(value,na.rm = TRUE)),by=c("Model","Sector", "RED")]
FINEREDTABminmax$Variable <- "Energy Use"

## PRODUCTVOLUME
PRODVOLTAB=ALLVAR[Variable %in% c("Chemical|HVC|Total Demand",
                                  "Pulp and Paper|Total",
                                  "Iron and Steel|Crude Steel",
                                  "Food Processing|Total"
) & Year %in% c("2015", "2030","2050") & Region=="EU28"]
PRODVOLTAB$Variable <- gsub("Production|Industry|", "", PRODVOLTAB$Variable, fixed=TRUE)
PRODVOLTAB$Variable <- gsub("|HVC|Total Demand", "", PRODVOLTAB$Variable, fixed=TRUE)
PRODVOLTAB$Variable <- gsub("|Total", "", PRODVOLTAB$Variable, fixed=TRUE)
PRODVOLTAB$Variable <- gsub("|Crude Steel", "", PRODVOLTAB$Variable, fixed=TRUE)

setnames(PRODVOLTAB,"Variable", "Sector")
PRODVOLTAB=spread(PRODVOLTAB, Year, value)
setnames(PRODVOLTAB, "2015", "X2015")
setnames(PRODVOLTAB, "2030", "X2030")
setnames(PRODVOLTAB, "2050", "X2050")
PRODVOLTABRED=PRODVOLTAB %>% mutate(RED2050=(1-(X2050/X2015))*100, RED2030=(1-(X2030/X2015))*100)

PRODVOLTABRED = rbind(WISEECO2[Variable=="Production", c("Model","Sector", "Scenario",  "RED2030", "RED2050")],PRODVOLTABRED[, c("Sector", "Scenario", "Model", "RED2030", "RED2050")] )
PRODVOLTABRED=PRODVOLTABRED[Sector=="Chemical", Sector:=c("Chemicals and Petrochemicals")]
PRODVOLTABRED2=gather(PRODVOLTABRED, RED, value, c(RED2030, RED2050))
PRODVOLTABRED2=data.table(PRODVOLTABRED2)
PRODVOLTABRED2=rbind(PRODVOLTABRED2, data.table(Model=c("WISEE", "WISEE"),
                                                Sector=c("Food Processing","Food Processing"),
                                                Scenario=c("CIRC", "CCS"),
                                                RED=c("RED2030", "RED2050"),
                                                value=c(0,0)))

PRODVOLTABREDminmax=PRODVOLTABRED2[!Scenario=="Baseline",list(ymax=max(value,na.rm = TRUE),ymin=min(value,na.rm = TRUE)),by=c("Model","Sector", "RED")]
PRODVOLTABREDminmax$Variable <- "Production volume"


###

MINMAX2050=ggplot()+
  geom_crossbar(data=CO2REDTABminmax[RED=="RED2050"], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model), width=.7, position=position_dodge(width=0.7))+
  
  annotate("rect", xmin=-Inf,xmax=Inf,ymin=0,ymax=100, fill="lightgrey", alpha=0.6) +
  annotate("rect", xmin=-Inf,xmax=Inf,ymin=100,ymax=Inf, fill="lightblue", alpha=0.6) +
  annotate("text", x=1.3,y=104, label="Net negative", size=3, angle=90, colour="dimgrey", hjust=0) +
  annotate("text", x=1.3, y=35, label="Reductions", size=3, angle=90, colour="dimgrey",  hjust=0) +
  annotate("text", x=1.3, y=-5, label="Increase", size=3, angle=90, colour="dimgrey",  hjust=1) +
  geom_crossbar(data=CO2REDTABminmax[RED=="RED2050"], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model),  width=.7, position=position_dodge(width=0.7))+
  
  geom_crossbar(data=FINEREDTABminmax[RED=="RED2050"], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model),  width=.7, position=position_dodge(width=0.7))+
  geom_crossbar(data=PRODVOLTABREDminmax[RED=="RED2050"], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model),  width=.7, position=position_dodge(width=0.7))+

  geom_hline(yintercept=100)+
  geom_hline(yintercept=0)+
  
   ggtitle(bquote("Indexed change in 2050 compared to 2015")) +
  xlab("\n \n \n \n Industry sector") + ylab("% Reduction \n ")+
  facet_wrap(~Variable)+
  scale_fill_manual(
    breaks=c("IMAGE", "WISEE"),
    values=c('blue', '#2ca25f'))+
  scale_colour_manual(
    breaks=c("IMAGE", "WISEE"),
    values=c('blue', '#2ca25f')) +
  guides(colour = element_blank()) +
  scale_x_discrete(breaks=c("Iron and Steel", "Chemicals and Petrochemicals", "Pulp and Paper", "Food Processing"),
                   labels=c("Steel",  "Chemicals","Paper", "Food")) +
  
  coord_cartesian(ylim=c(-40:150)) +
  theme_bw() +

  theme(
        axis.text.x = element_text(angle = 45, size=12,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF")
    )

ggplotly(MINMAX2050)

```

## Something about speed of change

Sometimes it is difficult to present transitions in a 2D environment. Visualizing the speed of time, and how different models respond cannot be displayed in a static visualization. So below the same image as above, just with the timescale as a running element in the animation:

```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.align="center", fig.width=10, fig.height=5, fig.cap="_**Figure**: Speed of change visualized for EU industry(represented in % change for each year)_"}

library(plotly)
library(ggplot2)
library(data.table)
library(dplyr)
library(tidyr)


WISEECO2_0= read.csv("data/WISEE_CO2_emissions_22_6_2018.csv", sep=";", dec=",")
WISEECO2=melt(WISEECO2_0,  id.vars=c("Model", "Sector", "Variable","Scenario"), variable.name="Year")
WISEECO2$Year = as.numeric(as.character(substr(WISEECO2$Year, 2, stop=100)))
WISEECO2$value = as.numeric(WISEECO2$value)
#WISEECO2 <- na.omit(WISEECO2)
WISEECO2=data.table(WISEECO2)
WISEECO2015=WISEECO2[Year=="2015"]
WISEECO2=merge(WISEECO2,WISEECO2015, by=c("Model", "Sector", "Variable", "Scenario"), allow.cartesian=T)

WISEECO2 = WISEECO2 %>% mutate(RED=(1-(value.x/value.y))*100)
WISEECO2=data.table(WISEECO2)
WISEECO2=WISEECO2[Sector=="Chemical", Sector:=c("Chemicals and Petrochemicals")]

# IMAGE

ALLVAR=read.csv("data/Compilation_IMAGE_REINENT_everything.csv", sep=";", dec=".")
ALLVAR$value <- as.numeric(ALLVAR$value)
ALLVAR$Year <- as.numeric(ALLVAR$Year)
ALLVAR=data.table(ALLVAR)

CO2TAB= ALLVAR[ Variable %in% c(
                  "Emissions|CO2|Iron and Steel|Direct emissions",
                  "Emissions|CO2|Pulp and Paper|Direct emissions", 
                  "Emissions|CO2|Chemicals and Petrochemicals|Direct emissions",
                  "Emissions|CO2|Food Processing|Direct emissions"
                ) & Region=="EU28"]
CO2TAB$Variable <- gsub("|Direct emissions", "", CO2TAB$Variable, fixed=T )

CO2TAB$Variable <- gsub("Emissions|CO2|", "", CO2TAB$Variable, fixed=T )
CO2TAB2015=CO2TAB[Year=="2015"]
CO2TAB=merge(CO2TAB, CO2TAB2015, by=c("Variable", "Scenario", "Unit", "Model", "Region"), allow.cartesian = T)

CO2TAB=CO2TAB %>% mutate(RED=(1-(value.x/value.y))*100)
setnames(CO2TAB, "Variable", "Sector")

CO2REDTAB = rbind(WISEECO2[Variable=="Emissions|CO2", c("Model","Sector", "Scenario","Year.x", "RED")],CO2TAB[, c("Sector", "Scenario", "Model", "Year.x", "RED")] )

#write.table(file="datatables/overview_table_indicators_CO2RED.csv", CO2REDTAB2, sep=",", dec=".", row.names=FALSE)
CO2REDTAB2=rbind(CO2REDTAB, data.table(Model=c("WISEE", "WISEE"),
                                                Sector=c("Food Processing","Food Processing"),
                                                Scenario=c("CIRC", "CCS"),
                                                 RED=c(0, 0),
                                                Year.x=c(2015, 2015)))
CO2REDTAB2=data.table(CO2REDTAB2)
CO2REDTABminmax=CO2REDTAB2[!Scenario=="Baseline",list(ymax=max(RED,na.rm = TRUE),ymin=min(RED,na.rm = TRUE)),by=c("Model","Sector", "Year.x")]
CO2REDTABminmax$Variable <- "CO2 Emissions"

## FINAL ENERGY REDUCTIONS
FINETABRED=ALLVAR[Variable %in% c("Final Energy|Industry|Pulp and Paper",
                                  "Final Energy|Industry|Iron and Steel",
                                  "Final Energy|Industry|Chemicals and Petrochemicals",
                                  "Final Energy|Industry|Food Processing"
) & Region=="EU28"]
FINETABRED$Variable <- gsub("Final Energy|Industry|", "", FINETABRED$Variable, fixed=TRUE)
setnames(FINETABRED,"Variable", "Sector")
FINETABRED2015=FINETABRED[Year=="2015"]
FINETABRED=merge(FINETABRED, FINETABRED2015, by=c("Sector", "Scenario", "Unit", "Model", "Region"), allow.cartesian = T)

FINETABRED=FINETABRED %>% mutate(RED=(1-(value.x/value.y))*100)
FINETABRED=data.table(FINETABRED)

FINEREDTAB2 = rbind(WISEECO2[Variable=="Final Energy", c("Model","Sector", "Scenario","Year.x", "RED")],FINETABRED[, c("Sector", "Scenario", "Model", "Year.x", "RED")] )
FINEREDTAB2=data.table(FINEREDTAB2)

FINEREDTAB2=rbind(FINEREDTAB2, data.table(Model=c("WISEE", "WISEE"),
                                        Sector=c("Food Processing","Food Processing"),
                                        Scenario=c("CIRC", "CCS"),
                                        RED=c(0, 0),
                                                Year.x=c(2015, 2015)))

FINEREDTABminmax=FINEREDTAB2[!Scenario=="Baseline",list(ymax=max(RED,na.rm = TRUE),ymin=min(RED,na.rm = TRUE)),by=c("Model","Sector", "Year.x")]
FINEREDTABminmax$Variable <- "Energy Use"

## PRODUCTVOLUME
PRODVOLTAB=ALLVAR[Variable %in% c("Chemical|HVC|Total Demand",
                                  "Pulp and Paper|Total",
                                  "Iron and Steel|Crude Steel",
                                  "Food Processing|Total"
) &  Region=="EU28"]
PRODVOLTAB$Variable <- gsub("Production|Industry|", "", PRODVOLTAB$Variable, fixed=TRUE)
PRODVOLTAB$Variable <- gsub("|HVC|Total Demand", "", PRODVOLTAB$Variable, fixed=TRUE)
PRODVOLTAB$Variable <- gsub("|Total", "", PRODVOLTAB$Variable, fixed=TRUE)
PRODVOLTAB$Variable <- gsub("|Crude Steel", "", PRODVOLTAB$Variable, fixed=TRUE)

setnames(PRODVOLTAB,"Variable", "Sector")

PRODVOLTAB2015=PRODVOLTAB[Year=="2015"]
PRODVOLTAB=merge(PRODVOLTAB, PRODVOLTAB2015, by=c("Sector", "Scenario", "Unit", "Model", "Region"), allow.cartesian = T)

PRODVOLTABRED=PRODVOLTAB %>% mutate(RED=(1-(value.x/value.y))*100)

PRODVOLTABRED = rbind(WISEECO2[Variable=="Production", c("Model","Sector", "Scenario", "Year.x", "RED")],PRODVOLTABRED[, c("Sector", "Scenario", "Model", "Year.x","RED")] )

PRODVOLTABRED=PRODVOLTABRED[Sector=="Chemical", Sector:=c("Chemicals and Petrochemicals")]
PRODVOLTABRED=data.table(PRODVOLTABRED)
PRODVOLTABRED2=rbind(PRODVOLTABRED, data.table(Model=c("WISEE", "WISEE"),
                                                Sector=c("Food Processing","Food Processing"),
                                                Scenario=c("CIRC", "CCS"),
                                                RED=c(0, 0),
                                                Year.x=c(2015, 2015)))

PRODVOLTABREDminmax=PRODVOLTABRED2[!Scenario=="Baseline",list(ymax=max(RED,na.rm = TRUE),ymin=min(RED,na.rm = TRUE)),by=c("Model","Sector", "Year.x")]
PRODVOLTABREDminmax$Variable <- "Production volume"

options(digits=0)
###

MINMAX=ggplot()+
  geom_crossbar(data=CO2REDTABminmax[Year.x %in% c(2015:2050)], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model), width=.7, position=position_dodge(width=0.7))+
  #
  annotate("rect", xmin=-Inf,xmax=Inf,ymin=0,ymax=100, fill="lightgrey", alpha=0.6) +
  annotate("rect", xmin=-Inf,xmax=Inf,ymin=100,ymax=Inf, fill="lightblue", alpha=0.6) +
  annotate("text", x=0.7,y=104, label="Net negative", size=3, angle=90, colour="dimgrey", hjust=0) +
  annotate("text", x=0.7, y=35, label="Reductions", size=3, angle=90, colour="dimgrey",  hjust=0) +
  annotate("text", x=0.7, y=-5, label="Increase", size=3, angle=90, colour="dimgrey",  hjust=1) +
  geom_crossbar(data=CO2REDTABminmax[Year.x %in% c(2015:2050)], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model),  width=.7, position=position_dodge(width=0.7))+
  
  geom_crossbar(data=FINEREDTABminmax[Year.x %in% c(2015:2050)], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model),  width=.7, position=position_dodge(width=0.7))+
  geom_crossbar(data=PRODVOLTABREDminmax[Year.x %in% c(2015:2050)], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model),  width=.7, position=position_dodge(width=0.7))+

  geom_hline(yintercept=100)+
  geom_hline(yintercept=0)+
  
   ggtitle(bquote("Indexed change in 2050 compared to 2015")) +
  xlab("\n \n \n \n Industry sector") + ylab("% Reduction \n ")+
  facet_wrap(~Variable)+
  scale_fill_manual(
    breaks=c("IMAGE", "WISEE"),
    values=c('blue', '#2ca25f'))+
  scale_colour_manual(
    breaks=c("IMAGE", "WISEE"),
    values=c('blue', '#2ca25f')) +
  guides(colour = element_blank()) +
  scale_x_discrete(breaks=c("Iron and Steel", "Chemicals and Petrochemicals", "Pulp and Paper", "Food Processing"),
                   labels=c("Steel",  "Chemicals","Paper", "Food")) +
  
  coord_cartesian(ylim=c(-40:150)) +
  theme_bw() +

  theme(
        axis.text.x = element_text(angle = 45, size=12,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF")
    )


library("gganimate")
library("gifski")
library("glue")

MINMAXanimate <- MINMAX +
                transition_components(Year.x) +
                labs(title = 'Year: {frame_time}')
MINMAXanimate

```

Here is the same result (IMAGE only) presenting the speed of industrial change across various major economies. It shows which regions fall through the floor (increase), or which of them could accelerate through the roof (deep decarbonization). The length of the bars represent the 'drag' between 2C or 1.5C - the longer the bar, the more efforts are required to bridge the gap between the 2C or 1.5C climate ambition.

```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.align="center", fig.width=10, fig.height=5, fig.cap="_**Figure**: Speed of change visualized for industry for the major economies (represented in % change for each year)_"}

library(plotly)
library(ggplot2)
library(data.table)
library(dplyr)
library(tidyr)
library(forcats)

# IMAGE

ALLVAR=read.csv("data/Compilation_IMAGE_REINENT_everything.csv", sep=";", dec=".")
ALLVAR=data.table(ALLVAR)

INDICATORSPROD=ALLVAR[Variable %in% c("Chemical|HVC|Total Demand",
                                      "Pulp and Paper|Total",
                                      "Iron and Steel|Crude Steel",
                                      "Food Processing|Total")]
INDICATORSPROD$Indicator <- "Production"
INDICATORSPROD$Variable <- gsub("|Total", "", INDICATORSPROD$Variable, fixed=T )
INDICATORSPROD$Variable <- gsub("|Crude Steel", "", INDICATORSPROD$Variable, fixed=T )
INDICATORSPROD$Variable <- gsub("|HVC Demand", "", INDICATORSPROD$Variable, fixed=T )


INDICATORS= ALLVAR[ Variable %in% c(
                  "Emissions|CO2|Iron and Steel|Direct emissions",
                  "Emissions|CO2|Pulp and Paper|Direct emissions", 
                  "Emissions|CO2|Chemicals and Petrochemicals|Direct emissions",
                  "Emissions|CO2|Food Processing|Direct emissions",
                  "Final Energy|Industry|Pulp and Paper",
                                  "Final Energy|Industry|Iron and Steel",
                                  "Final Energy|Industry|Chemicals and Petrochemicals",
                                  "Final Energy|Industry|Food Processing"
                ) ]
INDICATORS$Variable <- gsub("|Direct emissions", "", INDICATORS$Variable, fixed=T )
INDICATORS$Variable <- gsub("CO2|", "", INDICATORS$Variable, fixed=T )
INDICATORS$Variable <- gsub("Industry|", "", INDICATORS$Variable, fixed=T )

INDICATORSsplit<- data.frame(do.call('rbind', strsplit(as.character(INDICATORS$Variable),'|',fixed=TRUE)))
INDICATORS=cbind(INDICATORS,INDICATORSsplit$X1, INDICATORSsplit$X2)
INDICATORS$Variable <- NULL
setnames(INDICATORS, "V2", "Indicator")
setnames(INDICATORS, "V3", "Variable")

INDICATORS = rbind(INDICATORS, INDICATORSPROD)

INDICATORS2015=INDICATORS[Year=="2015"]
INDICATORS=merge(INDICATORS, INDICATORS2015, by=c("Variable", "Indicator","Scenario", "Unit", "Model", "Region"), allow.cartesian = T)

INDICATORS=INDICATORS %>% mutate(RED=(1-(value.x/value.y))*100)
setnames(INDICATORS, "Variable", "Sector")

INDICATORS=data.table(INDICATORS)
INDICATORSminmax=INDICATORS[!Scenario=="Baseline",list(ymax=max(RED,na.rm = TRUE),ymin=min(RED,na.rm = TRUE)),by=c("Model", "Sector","Indicator", "Region", "Unit", "Year.x")]
INDICATORSminmax=INDICATORSminmax[Sector=="Chemical", Sector:=c("Chemicals and Petrochemicals")]

INDICATORSminmax = INDICATORSminmax %>% mutate(
                          Sector=
                            fct_relevel(Sector, "Iron and Steel",  "Pulp and Paper", "Chemicals and Petrochemicals","Food Processing")
                            )
INDICATORSminmax=data.table(INDICATORSminmax)
options(digits=0)
###

MINMAXreg=ggplot()+
  geom_crossbar(data=INDICATORSminmax[Year.x %in% c(2015:2050)], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Region, colour=Region), width=.7, position=position_dodge(width=0.7))+
  #
  annotate("rect", xmin=-Inf,xmax=Inf,ymin=0,ymax=100, fill="lightgrey", alpha=0.6) +
  annotate("rect", xmin=-Inf,xmax=Inf,ymin=100,ymax=Inf, fill="lightblue", alpha=0.6) +
  annotate("text", x=0.7,y=104, label="Net negative", size=3, angle=90, colour="dimgrey", hjust=0) +
  annotate("text", x=0.7, y=35, label="Reductions", size=3, angle=90, colour="dimgrey",  hjust=0) +
  annotate("text", x=0.7, y=-5, label="Increase", size=3, angle=90, colour="dimgrey",  hjust=1) +
  geom_crossbar(data=INDICATORSminmax[Year.x %in% c(2015:2050)], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Region, colour=Region), width=.7, position=position_dodge(width=0.7))+
   
 
  geom_hline(yintercept=100)+
  geom_hline(yintercept=0)+
  
   ggtitle(bquote("Indexed change in 2050 compared to 2015")) +
  xlab("\n \n \n \n Industry sector") + ylab("% Reduction \n ")+
   facet_wrap(~Indicator)+
  scale_fill_manual(
    breaks=c("BRA", "CHN", "EU28", "INDIA", "USA", "World"),
    values=c('#d7191c','#fdae61','#2ca25f','#abd9e9','#2c7bb6', 'black'))+
  scale_colour_manual(
    breaks=c("BRA", "CHN", "EU28", "INDIA", "USA", "World"),
    values=c('#d7191c','#fdae61','#2ca25f','#abd9e9','#2c7bb6', 'black')) +
  guides(colour = element_blank()) +
  scale_x_discrete(breaks=c("Iron and Steel", "Chemicals and Petrochemicals", "Pulp and Paper", "Food Processing"),
                   labels=c("Steel",  "Chemicals","Paper", "Food")) +
  
  coord_cartesian(ylim=c(-40:150)) +
  theme_bw() +

  theme(
        axis.text.x = element_text(angle = 45, size=12,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF")
    )

#print(MINMAXreg)

library("gganimate")
library("gifski")
library("glue")

MINMAXreg.animate <- MINMAXreg +
                transition_time(Year.x) +
                labs(title = 'Year: {frame_time}')
MINMAXreg.animate

```


## Electrification, Biofuels and CCS 

The [REINVENT](http://www.reinvent-project.eu) quantitative models depict a variety of strategies to overcome technological lock-in while meeting the climate objective, including, **energy efficiency, biofuels, electrification** of processes or utilizing renewable power to produce feedstock or synthetic fuel (e.g. hydrogen) and **carbon capture & storage** (CCS). **End-use sectors** also contribute via recycling.


```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.align="center", fig.width=8, fig.height=4, fig.cap="_**Figure**: Available strategies to reach (full) decarbonisation in industry (in % application)_"}

library(plotly)
library(ggplot2)
library(data.table)
library(dplyr)

CONCLUSIONS0=read.csv("data/D42_conclusions.csv", sep=";", dec=",")
CONCLUSIONS=data.table(CONCLUSIONS0)
CONCLUSIONS=CONCLUSIONS[!Scenario=="Baseline"]
CONCLUSIONS=melt(CONCLUSIONS, id.vars = c("Model", "Scenario", "Indicator", "Unit"), variable.name = c("Sector"))
CONCLUSIONS$value <- as.numeric(CONCLUSIONS$value)
CONCLUSIONS = CONCLUSIONS %>%  mutate(value = if_else(is.na(value), 0, value))
CONCLUSIONS=data.table(CONCLUSIONS)

CONCLUSIONSminmax=CONCLUSIONS[,list(ymax=max(value,na.rm = TRUE),ymin=min(value,na.rm = TRUE)),by=c("Model","Sector", "Indicator")]
CONCLUSIONSminmax$Sector <- factor(CONCLUSIONSminmax$Sector, levels=unique(CONCLUSIONSminmax$Sector), labels=c("Steel", "Paper", "Chemicals", "Food"))



MINMAXCONC2050=ggplot()+
  geom_crossbar(data=CONCLUSIONSminmax[!Indicator=="CCS"], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model), width=.7, position=position_dodge(width=0.7))+
  
  annotate("rect", xmin=-Inf,xmax=Inf,ymin=0,ymax=100, fill="lightgrey", alpha=0.6) +
# annotate("rect", xmin=-Inf,xmax=Inf,ymin=100,ymax=Inf, fill="lightblue", alpha=0.6) +
# annotate("text", x=0.6,y=109, label="Net negative", size=3, angle=90, colour="dimgrey", hjust=0) +
 annotate("text", x=1, y=95, label="High use", size=3, angle=90, colour="dimgrey",  hjust=1) + 
  annotate("text", x=1, y=5, label="Low use", size=3, angle=90, colour="dimgrey",  hjust=0) + 
  geom_crossbar(data=CONCLUSIONSminmax[!Indicator=="CCS"], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Model, colour=Model), stat="identity",  width=.7, position=position_dodge(width=0.7))+
  
  geom_hline(yintercept=100)+
  geom_hline(yintercept=0)+
  
  ggtitle(bquote("Relative change in 2050 compared to 2015")) +
  xlab(" \n \n \n Industry sector") + ylab("% application \n ")+
  facet_wrap(~Indicator, nrow=1)+
  scale_fill_manual(
    breaks=c("IMAGE", "WISEE"),
    values=c('#2ca25f','blue')) +
  scale_colour_manual(
    breaks=c("IMAGE", "WISEE"),
    values=c('#2ca25f','blue')) +
  guides(colour = element_blank()) +
  coord_cartesian(ylim=c(-0:100)) +
  theme_bw() +
  theme(
        axis.text.x = element_text(angle = 45, size=12,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF")
    
        )

ggplotly(MINMAXCONC2050)  %>% 
 layout( 
 xaxis = list(automargin=TRUE), 
 yaxis = list(automargin=TRUE)
 )

```

Animate!


```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.align="center", fig.width=10, fig.height=5, fig.cap="_**Figure**: Speed of change visualized for industry for the major economies (representing the application of certain strategy in % for each year) (IMAGE only)_"}

library(plotly)
library(ggplot2)
library(data.table)
library(dplyr)
library(tidyr)
library(forcats)

# IMAGE

ALLVAR=read.csv("data/Compilation_IMAGE_REINENT_everything.csv", sep=";", dec=".", fileEncoding="latin1")
ALLVAR=data.table(ALLVAR)

####### IMAGE ONLY
FINETOTTAB=ALLVAR[Variable %in% c("Final Energy|Industry"
                                        ) & Year %in% c("2030", "2050") & Region=="EU28"]
FINETAB=ALLVAR[Variable %in% c("Final Energy|Industry|Pulp and Paper",
                               "Final Energy|Industry|Iron and Steel",
                               "Final Energy|Industry|Chemicals and Petrochemicals",
                               "Final Energy|Industry|Food Processing"
                              ) ]
FINETAB$Variable<- gsub("Final Energy|Industry|", "", FINETAB$Variable, fixed=T)
setnames(FINETAB, "Variable", "Sector")

ELECTRIFTAB=ALLVAR[Variable %in% c("Final Energy|Industry|Pulp and Paper|Electricity",
                                   "Final Energy|Industry|Iron and Steel|Electricity",
                                   "Final Energy|Industry|Chemicals and Petrochemicals|Electricity",
                                   "Final Energy|Industry|Food Processing|Electricity"
                                   ) ]
ELECTRIFTAB$Indicator<-"Electrification"

BIOTAB=ALLVAR[Variable %in% c("Final Energy|Industry|Pulp and Paper|Modern Biofuel",
                                   "Final Energy|Industry|Pulp and Paper|Secondary Heat",
                                   "Final Energy|Industry|Iron and Steel|Modern Biofuel",
                                   "Final Energy|Industry|Iron and Steel|Traditional Biofuel",
                                   "Final Energy|Industry|Chemicals and Petrochemicals|Modern Biofuel",
                                   "Final Energy|Industry|Chemicals and Petrochemicals|Traditional Biofuel",
                                   "Final Energy|Industry|Food Processing|Modern Biofuel",
                                   "Final Energy|Industry|Food Processing|Traditional Biofuel"
                                   
                                ) ]
BIOTAB$Indicator <- "Biofuels"
FOSSILTAB= ALLVAR[ Variable %in% c(
                        "Final Energy|Industry|Chemicals and Petrochemicals|Coal",
                        "Final Energy|Industry|Chemicals and Petrochemicals|Liquid Fuel",
                        "Final Energy|Industry|Chemicals and Petrochemicals|Gaseous Fuel",
                        "Final Energy|Industry|Pulp and Paper|Coal",
                        "Final Energy|Industry|Pulp and Paper|Liquid Fuel",
                        "Final Energy|Industry|Pulp and Paper|Gaseous Fuel",
                        "Final Energy|Industry|Food Processing|Coal",
                        "Final Energy|Industry|Food Processing|Liquid Fuel",
                        "Final Energy|Industry|Food Processing|Gaseous Fuel",
                        "Final Energy|Industry|Iron and Steel|Coal",
                        "Final Energy|Industry|Iron and Steel|Liquid Fuel",
                        "Final Energy|Industry|Iron and Steel|Gaseous Fuel"
                        
                        ) ]

FOSSILTAB$Indicator <- "Fossil fuel"

ENERGYTABOVERVIEW <- rbind(ELECTRIFTAB,BIOTAB, FOSSILTAB)
ENERGYTABOVERVIEW$Variable <- gsub("Final Energy|Industry|","", ENERGYTABOVERVIEW$Variable, fixed=TRUE)

ENERGYTABOVERVIEWsplit= data.frame(do.call('rbind', strsplit(as.character(ENERGYTABOVERVIEW$Variable),'|',fixed=TRUE)))
ENERGYTABOVERVIEWnew=cbind(ENERGYTABOVERVIEW,ENERGYTABOVERVIEWsplit$X1, ENERGYTABOVERVIEWsplit$X2)
setnames(ENERGYTABOVERVIEWnew, "V2", "Sector")
setnames(ENERGYTABOVERVIEWnew, "V3", "Carrier")

ENERGYTABOVERVIEWnewsum=ENERGYTABOVERVIEWnew[, sum(value, na.rm=T), by=c("Scenario", "Year", "Region", "Sector","Indicator")]
ENERGYTABOVERVIEWnewsumcalc= merge(ENERGYTABOVERVIEWnewsum,FINETAB, by=c("Scenario", "Year", "Region", "Sector"))
ENERGYTABOVERVIEWnewsumcalc = ENERGYTABOVERVIEWnewsumcalc %>% mutate(Share=(V1/value)*100)

ENERGYTABOVERVIEWnewsumcalc$V1 <- NULL
ENERGYTABOVERVIEWnewsumcalc$value <- NULL

## Hijack
ENERGYTABOVERVIEWnewsumcalcplot=ENERGYTABOVERVIEWnewsumcalc
#/Hijack

#Hijack, taken from Row 4500 or something
ENERGYTABOVERVIEWnewsumcalcplot=data.table(ENERGYTABOVERVIEWnewsumcalcplot)
ENERGYTABOVERVIEWnewsumcalcplot2=ENERGYTABOVERVIEWnewsumcalcplot[!Scenario=="Baseline"]
ENERGYTABOVERVIEWnewsumcalcplot2minmax=ENERGYTABOVERVIEWnewsumcalcplot2[,list(ymax=max(Share,na.rm = TRUE),ymin=min(Share,na.rm = TRUE)),by=c("Model","Sector", "Indicator", "Year", "Region")]

ENERGYTABOVERVIEWnewsumcalcplot2minmax =ENERGYTABOVERVIEWnewsumcalcplot2minmax %>% mutate(Sector =
                                                                                  fct_relevel(Sector, 
                                                                                              "Iron and Steel",  
                                                                                              "Pulp and Paper", 
                                                                                              "Chemicals and Petrochemicals",
                                                                                              "Food Processing"))
ENERGYTABOVERVIEWnewsumcalcplot2minmax=data.table(ENERGYTABOVERVIEWnewsumcalcplot2minmax)
###

STRATMINMAXreg=ggplot()+
  geom_crossbar(data=ENERGYTABOVERVIEWnewsumcalcplot2minmax[Year %in% c(2015:2050)], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Region, colour=Region), width=.7, position=position_dodge(width=0.7))+
  #
    annotate("rect", xmin=-Inf,xmax=Inf,ymin=0,ymax=100, fill="lightgrey", alpha=0.6) +
# annotate("rect", xmin=-Inf,xmax=Inf,ymin=100,ymax=Inf, fill="lightblue", alpha=0.6) +
# annotate("text", x=0.6,y=109, label="Net negative", size=3, angle=90, colour="dimgrey", hjust=0) +
 annotate("text", x=0.6, y=95, label="High use", size=3, angle=90, colour="dimgrey",  hjust=1) + 
  annotate("text", x=0.6, y=5, label="Low use", size=3, angle=90, colour="dimgrey",  hjust=0) + 
  geom_crossbar(data=ENERGYTABOVERVIEWnewsumcalcplot2minmax[Year %in% c(2015:2050)], aes(x=Sector, ymin=ymin, ymax=ymax, y=ymax, fill=Region, colour=Region), width=.7, position=position_dodge(width=0.7))+
   
 
  geom_hline(yintercept=100)+
  geom_hline(yintercept=0)+
  
   ggtitle(bquote("Indexed change in 2050 compared to 2015")) +
  xlab("\n \n \n \n Industry sector") + ylab("% Application in total FE \n ")+
   facet_wrap(~Indicator)+
  scale_fill_manual(
    breaks=c("BRA", "CHN", "EU28", "INDIA", "USA", "World"),
    values=c('#d7191c','#fdae61','#2ca25f','#abd9e9','#2c7bb6', 'black'))+
  scale_colour_manual(
    breaks=c("BRA", "CHN", "EU28", "INDIA", "USA", "World"),
    values=c('#d7191c','#fdae61','#2ca25f','#abd9e9','#2c7bb6', 'black')) +
  guides(colour = element_blank()) +
  scale_x_discrete(breaks=c("Iron and Steel", "Chemicals and Petrochemicals", "Pulp and Paper", "Food Processing"),
                   labels=c("Steel",  "Chemicals","Paper", "Food")) +
  
  coord_cartesian(ylim=c(0:100)) +
  theme_bw() +

  theme(
        axis.text.x = element_text(angle = 45, size=12,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF")
    )

#print(STRATMINMAXreg)

library("gganimate")
library("gifski")
library("glue")

STRATMINMAXreg.animate <- STRATMINMAXreg +
                transition_time(Year) +
                labs(title = 'Year: {frame_time}')
STRATMINMAXreg.animate

```


Changing landscape towards 2050 {.tabset .tabset-fade #pathways}
-------------------------------------


For 2050 our analyses show that **close to zero** or even **negative emissions** are required in basic industries. However, **inertia of existing assets** and the **ramp up of low carbon infrastructures and technologies** seem to be underestimated in many studies. This may result in a **≥ doubling** of required **emission efficiency rates**.


```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE}

library(plotly)
library(ggplot2)
library(data.table)
library(dplyr)
library(tidyr)
library(gridExtra)


WISEECO2_0= read.csv("data/WISEE_CO2_emissions_22_6_2018.csv", sep=";", dec=",")
WISEECO2=melt(WISEECO2_0,  id.vars=c("Model", "Sector", "Variable","Scenario"), variable.name="Year")
WISEECO2$Year = as.numeric(as.character(substr(WISEECO2$Year, 2, stop=100)))
WISEECO2$value = as.numeric(WISEECO2$value)
#WISEECO2 <- na.omit(WISEECO2)
WISEECO2=data.table(WISEECO2)
setnames(WISEECO2, "Model", "Study")

WISEECO22010=WISEECO2[Year=="2015"]
WISEECO2= merge(WISEECO2, WISEECO22010, by=c("Study", "Sector", "Variable","Scenario"))
WISEECO2share=WISEECO2  %>% mutate(Index=(value.x/value.y)*100)
WISEECO2share=data.table(WISEECO2share)

# IMAGE

ALLVAR=read.csv("data/Compilation_IMAGE_REINENT_everything.csv", sep=";", dec=".", fileEncoding="latin1")
ALLVAR$value <- as.numeric(ALLVAR$value)
ALLVAR$Year <- as.numeric(ALLVAR$Year)
ALLVAR=data.table(ALLVAR)

  
CO2index=ALLVAR[Variable %in% c(  "Emissions|CO2|Iron and Steel|Direct emissions",
                                                                                                       "Emissions|CO2|Pulp and Paper|Direct emissions",
                                    "Emissions|CO2|Chemicals and Petrochemicals|Direct emissions",
                                    "Emissions|CO2|Food Processing|Direct emissions"
  )& Region %in% c("EU28") & Scenario %in% c("2 Degrees", "1.5 Degrees")]
  
  CO2index2010=CO2index[Year=="2010"]
  CO2indexcalc=merge(CO2index, CO2index2010, by=c("Variable","Scenario",  "Unit", "Model", "Region"))
  CO2indexcalc=CO2indexcalc %>% mutate(INDEX=(value.x/value.y)*100)
  CO2indexcalc=data.table(CO2indexcalc)
  CO2indexcalc=CO2indexcalc[Variable=="Emissions|CO2|Chemicals and Petrochemicals|Direct emissions", Variable:=c("Chemical")]
  CO2indexcalc=CO2indexcalc[Variable=="Emissions|CO2|Food Processing|Direct emissions", Variable:=c("Food")]
  CO2indexcalc=CO2indexcalc[Variable=="Emissions|CO2|Pulp and Paper|Direct emissions", Variable:=c("PPI")]
  CO2indexcalc=CO2indexcalc[Variable=="Emissions|CO2|Iron and Steel|Direct emissions", Variable:=c("Iron and Steel")]
  
  
  setnames(CO2indexcalc, "Model", "Study")
  ############## CO2 Emissions
  #################################################################
  # Data: CEFIC/Ecofys
  
  ###### CEFIC/Ecofys (2013) p. vii, read from graph)
  CEFICchem.emis=data.table(
    Year=c(2010,2020,2030,2050,2010,2020,2030,2050),
    Scenario=c("BL","BL","BL", "BL","n2DS","n2DS","n2DS","n2DS"),
    Chemical =c(240,375,330,440, 240, 180, 160,25) # MtCO2e /yr
  )
  
  CEFICchem.emis=gather(CEFICchem.emis, Sector, value, by=c("Chemical"))
  CEFICchem.emis$Variable <- "Final Energy|Industry"
  CEFICchem.emis$Study <- "CEFIC/Ecofys (2013)"
  CEFICchem.emis=data.table(CEFICchem.emis)
  
  #Y2010 
  CEFICchem.emis=merge(CEFICchem.emis,CEFICchem.emis[Scenario=="BL", -c("Scenario")], by=c("Year", "Sector", "Study", "Variable"))
  setnames(CEFICchem.emis, "value.y", "BL")
  CEFICchem.emis=merge(CEFICchem.emis, CEFICchem.emis[Year=="2010", -c("Year", "BL")], by=c("Scenario", "Sector", "Study", "Variable"))
  setnames(CEFICchem.emis, "value.x.x", "value")
  setnames(CEFICchem.emis, "value.x.y", "Y2010")
  # Replaced Y2005 with Y2015(IEA)
  CEFICchem.emis = CEFICchem.emis %>% mutate(ByBL=(value/BL)*100, ByY=(value/Y2010)*100, ByX=(BL/Y2010)*100)
  CEFICchem.emis=data.table(CEFICchem.emis)
  

  ###### Broeren et al. (2014) p. 281, read from graph)
  Broerenchem.emis=data.table(
    Year=c(2010,2030,2010,2030),
    Scenario=c("BL", "BL","n2DS","n2DS"),
    Chemical =c(0.75, 1.1, 0.75, 0.87) # GtCO2e /yr
  )
  
  Broerenchem.emis=gather(Broerenchem.emis, Sector, value, by=c("Chemical"))
  Broerenchem.emis$Variable <- "Emissions|CO2"
  Broerenchem.emis$Study <- "Broeren et al. (2014)"
  Broerenchem.emis=data.table(Broerenchem.emis)
  
  #Y2010 
  Broerenchem.emis=merge(Broerenchem.emis,Broerenchem.emis[Scenario=="BL", -c("Scenario")], by=c("Year", "Sector", "Study", "Variable"))
  setnames(Broerenchem.emis, "value.y", "BL")
  Broerenchem.emis=merge(Broerenchem.emis, Broerenchem.emis[Year=="2010", -c("Year", "BL")], by=c("Scenario", "Sector", "Study", "Variable"))
  setnames(Broerenchem.emis, "value.x.x", "value")
  setnames(Broerenchem.emis, "value.x.y", "Y2010")
  # Replaced Y2005 with Y2015(IEA)
  Broerenchem.emis = Broerenchem.emis %>% mutate(ByBL=(value/BL)*100, ByY=(value/Y2010)*100, ByX=(BL/Y2010)*100)
  Broerenchem.emis=data.table(Broerenchem.emis)
  
  
  # DECHEMA (2016) emissions in MtCO2 - required a calculation of BAU - RED (p108-111)
  DECHEMA.emis= data.table(
                    Year=c(rep(c(2015,	2030,	2050), 2)),	
                    Scenario=c("BL","BL","BL", "n2DS","n2DS","n2DS"),
                    Olefins=c(29,	33,	38,	29,	8,	-52)) #MtCO2
  
  DECHEMA.emis=gather(DECHEMA.emis, Sector, value, by=c("Olefins"))
  DECHEMA.emis$Variable <- "Emissions|CO2"
  DECHEMA.emis$Study <- "DECHEMA (2017)"
  DECHEMA.emis=data.table(DECHEMA.emis)
  
  #Y2010 
  DECHEMA.emis=merge(DECHEMA.emis,DECHEMA.emis[Scenario=="BL", -c("Scenario")], by=c("Year", "Sector", "Study", "Variable"))
  setnames(DECHEMA.emis, "value.y", "BL")
  DECHEMA.emis=merge(DECHEMA.emis, DECHEMA.emis[Year=="2015", -c("Year", "BL")], by=c("Scenario", "Sector", "Study", "Variable"))
  setnames(DECHEMA.emis, "value.x.x", "value")
  setnames(DECHEMA.emis, "value.x.y", "Y2015")
  # Replaced Y2005 with Y2015(IEA)
  DECHEMA.emis = DECHEMA.emis %>% mutate(ByBL=(value/BL)*100, ByY=(value/Y2015)*100, ByX=(BL/Y2015)*100)
  DECHEMA.emis=data.table(DECHEMA.emis)
  
  ## WSP  Reference, Max Tech & Max Tech no biomass (p. 64). Emission reductionss compared to 2012 (for "Current trends")
 WSP.emis= data.table(
    Year=c(rep(c(2010, 2020,	2030, 2040,	2050), 3)),	
    Scenario=c("BL","BL","BL", "BL","BL","n2DS","n2DS","n2DS","n2DS","n2DS","n2DSnb","n2DSnb","n2DSnb","n2DSnb","n2DSnb"),
    Chemical=c(100,	82,	81,	85,	90,
               100, 73,45, 18,12,
               100, 78, 64, 21, 20)) 

 WSP.emis=gather(WSP.emis, Sector, value, by=c("Chemical"))
 WSP.emis$Variable <- "Emissions|CO2"
 WSP.emis$Study <- "WSP/DNV-GL (2015)"
 WSP.emis=data.table(WSP.emis)
 
 #Y2010 
 WSP.emis=merge(WSP.emis,WSP.emis[Scenario=="BL", -c("Scenario")], by=c("Year", "Sector", "Study", "Variable"))
 setnames(WSP.emis, "value.y", "BL")
 WSP.emis=merge(WSP.emis, WSP.emis[Year=="2010", -c("Year", "BL")], by=c("Scenario", "Sector", "Study", "Variable"))
 setnames(WSP.emis, "value.x.x", "value")
 setnames(WSP.emis, "value.x.y", "Y2010")
 # Replaced Y2005 with Y2015(IEA)
 WSP.emis = WSP.emis %>% mutate(ByBL=(value/BL)*100,  ByX=(BL/Y2010)*100)
 setnames(WSP.emis, "value", "ByY")
 WSP.emis=data.table(WSP.emis)
  
# #D4.1 versions Steel and paper Clemens
D41STEEL=read.csv("data/D4_1_steel.csv", sep=";", dec=".", fileEncoding="latin1")
D41STEEL=data.table(D41STEEL)
D41STEEL = D41STEEL %>% mutate(index=(value2/value1)*100)
D41STEEL=data.table(D41STEEL)
setnames(D41STEEL, "Variable", "Indicator")
D41STEEL$Variable <- "Iron and Steel"


 ########## PPI emissions
D41PAPER=read.csv("data/D4_1_paper.csv", sep=";", dec=".")
D41PAPER=data.table(D41PAPER)
D41PAPER=D41PAPER %>% mutate(index=(value2/value1)*100)
D41PAPER=data.table(D41PAPER)
setnames(D41PAPER, "Variable", "Indicator")
D41PAPER$Variable <- "Pulp and Paper"

#################################################################
  ##################### FOOD  EMISSIONS  ##########################
  #################################################################
  
  WSP.foodemis=data.table(Year=c(rep(c(2010,2020,2030,2040,2050),3)),
                          Scenario=c(rep("BL", 5), rep("n2DS2noelec",5), rep("n2DS1", 5)),
                          Food=c(100,75,70,68,70,
                                      100, 67,56,45,35,
                                      100, 67, 53,37,25))
  
  WSP.foodemis=gather(WSP.foodemis, Sector, value, by=c("Food"))
  WSP.foodemis$Variable <- "Emissions|CO2"
  WSP.foodemis$Study <- "WSP/DNV-GL (2015b)"
  WSP.foodemis=data.table(WSP.foodemis)
  
  #Y2010 
  WSP.foodemis=merge(WSP.foodemis,WSP.foodemis[Scenario=="BL", -c("Scenario")], by=c("Year", "Sector", "Study", "Variable"))
  setnames(WSP.foodemis, "value.y", "BL")
  WSP.foodemis=merge(WSP.foodemis, WSP.foodemis[Year=="2010", -c("Year", "BL")], by=c("Scenario", "Sector", "Study", "Variable"))
  setnames(WSP.foodemis, "value.x.x", "value")
  setnames(WSP.foodemis, "value.x.y", "Y2010")
  # Replaced Y2005 with Y2015(IEA)
  WSP.foodemis = WSP.foodemis %>% mutate(ByBL=(value/BL)*100,  ByX=(BL/Y2010)*100)
  setnames(WSP.foodemis, "value", "ByY")
  WSP.foodemis=data.table(WSP.foodemis)
  ###################################
 ###################################
 ############Poster
```  

  
### Steel industry 
```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.cap="_**Figure:** 'Other studies' refer to: ALL10: Allwood et al. (2010), MIL13: Milford et al. (2013), IEA17: OECD/IEA (2017a), IEA09: OECD/IEA (2009), RUJ16: Van Ruijven et al. (2016), BEL09: Bellevrat and Menanteau (2009), SEI09: Heaps et al. (2009), BCG13: Boston Consulting Group/VDEh (2013), JRC12: Pardo et al. (2012), ARE16: Arens et al. (2016), WSP15: WSP Parsons Brunckerhoff / DNV GL (2015c), ROO14: Rootzén and Johnsson (2015)_"}
  
  INDTEELemisbyPoster=ggplot() +
    geom_hline(yintercept=100, linetype=2) +
    
    # Data Clemens????
    geom_line(data=D41STEEL[Indicator=="GHG Emissions"], aes(x=Target, y=index, group=Scenario), colour='darkgrey')+
    
    geom_hline(yintercept = 0, linetype=1, alpha=0.4) +
    
  #IMAGE
     geom_line(data=CO2indexcalc[Variable %in% c("Iron and Steel") & Region %in% c("EU28") & Scenario %in% c("2 Degrees", "1.5 Degrees") ], aes(x=Year.x, y=INDEX, group=Scenario, linetype=Scenario, colour=Study), size=1)+
    
    # WISEE
    geom_line(data=WISEECO2share[Sector=="Iron and Steel" & Variable=="Emissions|CO2"], aes(x=Year.x, y=Index, group=Scenario, linetype=Scenario, colour=Study), size=1) +
    
    # Other
    geom_line(data=data.table(Year.x=c(2020),
                              INDEX=c(0),
                              Scenario=c("2 Degrees"),
                              Study=c("Others"),
                              Sector=c("Iron and Steel")), aes(x=Year.x, y=INDEX, group=Scenario, linetype=Scenario, colour=Study), size=1)+
    
    #facet_wrap(~Sector, ncol=1) +
    coord_cartesian(xlim=c(2005:2050), ylim=c(0:150)) +
    theme_bw() +
    ggtitle(bquote(bold("Total"~CO[2]~"emissions"))) +
    labs(y="Index (2010=100) ", x = "Year") +
    guides(fill=guide_legend("Sector"))+
    scale_colour_manual(values=c('#2ca25f', "darkgrey",'blue'),
                        breaks=c( "IMAGE", "WISEE", "Others") ) +
    scale_linetype_manual(values=c(6,1,6,1)) +
     theme(
        axis.text.x = element_text(angle = 45, size=14,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF")
            ) 
  
#print(INDTEELemisbyPoster)
  ggplotly(INDTEELemisbyPoster)

```


### Chemical industry
```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
  #####
  INDCHEMemisbyPoster=ggplot() +
    geom_hline(yintercept=100, linetype=2) +
    
    #CEFIC/Ecofys (2013)
    geom_line(data=CEFICchem.emis[!Scenario=="BL" & Sector=="Chemical"], aes(x=Year, y=ByY,  group=Scenario), colour='darkgrey') +
    
    #Broeren et al. (2014)
    geom_line(data=Broerenchem.emis[!Scenario=="BL" & Sector=="Chemical"], aes(x=Year, y=ByY, group=Scenario), colour='darkgrey' ) +
    
    
    
    #WSP p. 64  this is UK based
    geom_line(data=WSP.emis[!Scenario=="BL" & Sector=="Chemical"], aes(x=Year, y=ByY,  group=Scenario), colour='darkgrey') +
    
    geom_hline(yintercept = 0, linetype=1, alpha=0.4) +
    #IMAGE
    geom_line(data=CO2indexcalc[Variable %in% c( "Chemical") & Region %in% c("EU28") & Scenario %in% c("2 Degrees", "1.5 Degrees") ], aes(x=Year.x, y=INDEX, group=Scenario, linetype=Scenario, colour=Study), size=1)+
    
    # WISEE
    geom_line(data=WISEECO2share[Sector=="Chemical" & Variable=="Emissions|CO2"], aes(x=Year.x, y=Index, group=Scenario, linetype=Scenario, colour=Study), size=1) +
    
    #facet_wrap(~Sector, ncol=1) +
    coord_cartesian(xlim=c(2005:2050), ylim=c(0:150)) +
    theme_bw() +
    ggtitle(bquote(bold("Total"~CO[2]~"emissions"))) +
    labs(y="Index (2010=100) ", x = "Year") +
    guides(fill=guide_legend("Sector"))+
    scale_colour_manual(values=c('#2ca25f','blue'),
                        breaks=c("IMAGE", "WISEE")
    ) +
    scale_linetype_manual(values=c(6,1,6,1)) +
    
    theme(
        axis.text.x = element_text(angle = 45, size=14,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF")
            ) 
  
  ggplotly(INDCHEMemisbyPoster)
```
  
### Pulp & paper industry
```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE}

  ##
  INDPPIemisbyPoster=ggplot() +
    geom_hline(yintercept=100, linetype=2) +
    
    # Data Clemens????
    # ??????????? Clemens data
    geom_line(data=D41PAPER[Indicator=="GHG Emissions"], aes(x=Target, y=index, group=Scenario), colour='darkgrey')+
    
    geom_hline(yintercept = 0, linetype=1, alpha=0.4) +
    #IMAGE
    geom_line(data=CO2indexcalc[Variable %in% c("Pulp and Paper") & Region %in% c("EU28") & Scenario %in% c("2 Degrees", "1.5 Degrees") ], aes(x=Year.x, y=INDEX, group=Scenario, linetype=Scenario, colour=Study), size=1)+
    
    # WISEE
    geom_line(data=WISEECO2share[Sector=="Pulp and Paper" & Variable=="Emissions|CO2"], aes(x=Year.x, y=Index, group=Scenario, linetype=Scenario, colour=Study), size=1) +
    
    
    #facet_wrap(~Sector, ncol=1) +
    coord_cartesian(xlim=c(2005:2050), ylim=c(-50:120)) +
    theme_bw() +
    ggtitle(bquote(bold("Total"~CO[2]~"emissions"))) +
    labs(y="Index (2010=100) ", x = "Year") +
    guides(fill=guide_legend("Sector"))+
    scale_colour_manual(values=c( '#2ca25f','blue'),
                        breaks=c( "IMAGE",  "WISEE")) +
    
    scale_linetype_manual(values=c(6,1,6,1)) +
     theme(
        axis.text.x = element_text(angle = 45, size=14,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF")
            ) 
  
  print(INDPPIemisbyPoster)
```

### Food industry

```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
  ###
 
  INDFOODemisbyPoster=ggplot() +
    geom_hline(yintercept=100, linetype=2) +
    
    #WSP p. 64  this is UK based
    geom_line(data=WSP.foodemis[!Scenario=="BL" & Sector=="Food"], aes(x=Year, y=ByY, colour=Study, group=Scenario), colour='grey' ) +
    #geom_line(data=WSP.foodemis[Scenario=="BL" & Sector=="Food"], aes(x=Year, y=ByX, colour=Study, group=Scenario), size=1, linetype=2 ) +
    
    #Audrey et al (2009) (WWF) all areas scenario.  this is UK based
    geom_line(data=data.table(Year=c(2010,2020,2030,2040,2050),
                              Study=c(rep("Audsley et al. (2009)",5)),
                              Scenario=c(rep("Decarbonisation", 5)),
                              ByY=c(100,79,62,48,30)), aes(x=Year, y=ByY,  group=Scenario), colour='grey' ) +
    
    #IMAGE
    geom_line(data=CO2indexcalc[Variable %in% c( "Food") & Region %in% c("EU28") & Scenario %in% c("2 Degrees", "1.5 Degrees") ], aes(x=Year.x, y=INDEX, group=Scenario, linetype=Scenario, colour=Study), size=1)+
    scale_colour_manual(values=c('#2ca25f'),
                        breaks=c( "IMAGE")
    ) +
    
    #facet_wrap(~Sector, ncol=1) +
    coord_cartesian(xlim=c(2005:2050), ylim=c(0:150)) +
    theme_bw() +
    ggtitle(bquote(bold("Total"~CO[2]~"emissions"))) +
    labs(y="Index (2010=100) ", x = "Year") +
    guides(fill=guide_legend("Sector"))+
     theme(
        axis.text.x = element_text(angle = 45, size=14,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF")
            ) 
  
  
  ggplotly(INDFOODemisbyPoster)                      
                        
 
  
```

-------------------------------------

## Invest in lock-in or structural change? 

Technical assets in several big industry clusters around Europe **are growing old**, creating a natural **window of opportunity** in the **next 1-2 decades**. Re-investing in Paris-proof processes and technologies will **need infrastructures** to supply **clean energy, technological innovation** and **risk taking investment decisions**. 

```{r results=TRUE, message=FALSE, warning=FALSE, echo=FALSE,WISEECO2, fig.align="center", fig.width=8, fig.height=4, fig.cap="_**Figure**: Capacity changes (Mt/yr) for the short-term (2015-2030), mid-term (2030-2040), and long-term (2040-2050). NWE contains NL, Be, Ger, Fra._"}

library(plotly)
library(ggplot2)
library(data.table)
library(dplyr)
### WISEE capacities Poster

WISEECAPACITYPOSTER=data.table(
  Region=c(	"AT",	"BE",	"DE",	"FI",	"FR",	"IT",	"NL",	"PL",	"SE",	"SK",	"SP",	"UK",	"AT",	"BE",	"DE",	"FI",	"FR",	"IT",	"NL",	"PL",	"SE",	"SK",	"SP",	"UK"	),
  Technology=c(	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace"	),
  Shortterm=c(	"0",	"-1.08",	"-2.333",	"-0.33",	"-0.99",	"-1.18",	"-2.14",	"-0.7",	"0",	"-0.22",	"-0.25",	"-1.17",	"0",	"0",	"-2",	"-1",	"0",	"0",	"0",	"0",	"0",	"0",	"0",	"-3.5"	),
  Midterm=c(	"0",	"-0.57",	"-3.075",	"0",	"-0.568",	"0",	"0",	"0",	"0",	"0",	"-1.18",	"-0.32",	"0",	"0",	"-15",	"-1",	"-6",	"-7",	"0",	"-7",	"-3",	"0",	"-5",	"-3.5"	),
  Longterm=c(	"-0.5",	"0",	"-0.58",	"0",	"-0.945",	"-0.38",	"-1.165",	"0",	"0",	"0",	"0",	"-0.73",	"0",	"-4",	"-17",	"0",	"-5",	"-1",	"-6",	"0",	"0",	"-4",	"0",	"-3"	))
  
WISEECAPACITYPOSTER=gather(WISEECAPACITYPOSTER, Period, value, c(Shortterm, Midterm, Longterm))
WISEECAPACITYPOSTER=data.table(WISEECAPACITYPOSTER)
WISEECAPACITYPOSTER$value=as.numeric(WISEECAPACITYPOSTER$value)

### WISEE capacities (Aggregated regions) Poster

WISEECAPACITYPOSTERaggr=data.table(
  Region=c(	"CEE",	"SE",	"NE",	"NWE",	"SEE",	"UK",	"CEE",	"SE",	"NE",	"NWE",	"SEE",	"UK"		),
  Technology=c(	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Steam Cracker",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace",	"Blast Furnace"		),
  Shortterm=c(	-1.58,	-1.43,	-0.33,	-6.543,	-0.2,	-1.17,	0,	0,	-1,	-2,	0,	-3.5		),
  Midterm=c(	0,	-1.18,	0,	-4.213,	0,	-0.32,	-8,	-12,	-4,	-21,	-4,	-3.5		),
  Longterm=c(	-0.5,	-0.38,	0,	-2.69,	0,	-0.73,	-4,	-1,	0,	-32,	0,	-3		)
  
  )
  
WISEECAPACITYPOSTERaggr=gather(WISEECAPACITYPOSTERaggr, Period, value, c(Shortterm, Midterm, Longterm))
WISEECAPACITYPOSTERaggr=data.table(WISEECAPACITYPOSTERaggr)
WISEECAPACITYPOSTERaggr$Period <- factor(WISEECAPACITYPOSTERaggr$Period, levels=c("Shortterm", "Midterm", "Longterm"), labels=c("2015-2030", "2030-2040", "2040-2050"))


## BAR chart
INDUSCAPCHANGEaggr=ggplot() +
  geom_bar(data=WISEECAPACITYPOSTERaggr, aes(x=Region, y=value,  fill=Period), colour='black', stat="identity", position="stack", width=.8)+
  
  facet_wrap(~Technology, scales="free_y") +
  theme_bw() +
  #coord_cartesian(ylim = c(0:12)) +
  ggtitle("Capacity changes") +
  labs(y="Capacity change (Mt/yr)  \n ", x = "\n \n \n Year") +
  guides(fill=guide_legend("Sector"))+
  scale_fill_manual(values=c('#2ca25f','blue', 'darkgrey')) +
  theme(
        axis.text.x = element_text(angle = 45, size=14,  hjust=1),
        axis.title.y = element_text(size=13),
        axis.title.x = element_text(size=13),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size=12, face="bold"),
        strip.text.y = element_text(size=12, face="bold"),
        legend.text= element_text(size=12),
        legend.title=element_text(size=13,  face="bold"),
        plot.title=element_text(size=16, hjust=0.5, face="bold"), 
        plot.subtitle=element_text(size=14,hjust=0.5),
        panel.border = element_rect(colour = "black", size=1),
        legend.key =  element_rect(fill = 'white', size = 0.5),
        strip.background = element_rect(colour="white", fill="#FFFFFF"),
        panel.spacing = unit(2, "lines")
    
        )


ggplotly(INDUSCAPCHANGEaggr)

```


## Smart Industrial policies needed 

Radical changes are needed in all major industrial clusters. To avoid fossil lock-ins, new low-carbon infrastructures and **joint technological visions** are **needed**. In globally competitive environments such a change needs **strong cooperation of public and private investment**. Linking with **demand side strategies** and **circularity** creates additional benefits and challenges.

## Moving beyond existing thinking... 

Clear **bottle-necks** have been observed in scenario studies assuming **business-as-usual operations** and **rising consumption patterns**. New [REINVENT](http://www.reinvent-project.eu) research is set out on exploring (1) the **break away** from current systems and (infra)structures and (2) opportunties **between** sectors, organisations and down the value chains.


