---
title: "REINVENT D4.4 Preliminary results"
author: "  TIMER_3_11, World results " 
output: html_document
---

```{r setup, include=FALSE}

#######################################################################################################################
# THIS FILE: Analyses all the REINVENT narrative scenarios
# DATE: May 2020
#######################################################################################################################

# # Clear memory
# rm(list=ls()) # clear memory
# 
# # Working directory
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
# 
setwd("/mnt/y/Kennisbasis/IMAGE/model/users/mariesse/R/GitHub/marieyesse.github.io-master/marieyesse.github.io")
#######################################################################################################################
### Install and/or load required packages / dependencies
#######################################################################################################################

# Easy scripting packages
if(!require(dplyr)){install.packages("dplyr");   library(dplyr)}
if(!require(forcats)){install.packages("forcats");  library(forcats)}
if(!require(data.table)){install.packages("data.table");  library(data.table)}
if(!require(tidyr)){install.packages("tidyr");  library(tidyr)}
if(!require(fuzzyjoin)){install.packages("fuzzyjoin");  library(fuzzyjoin)}
if(!require(stringr)){install.packages("stringr");  library(stringr)}
if(!require(rlang)){install.packages("rlang");  library(rlang)}
if(!require(readr)){install.packages("readr");  library(readr)}

# text mining packages
if(!require(tidytext)){install.packages("tidytext");  library(tidytext)}
if(!require(tm)){install.packages("tm");  library(tm)}
if(!require(readxl)){install.packages("readxl");  library(readxl)}
if(!require(tabulizer)){install.packages("tabulizer");  library(tabulizer)}

# maps
if(!require(grid)){install.packages("grid"); library(grid)}
if(!require(rworldmap)){install.packages("rworldmap");  library(rworldmap)}
if(!require(geosphere)){install.packages("geosphere"); library(geosphere)}
if(!require(gpclib)){install.packages("gpclib"); library(gpclib)}

# data visualisation packages
if(!require(ggplot2)){install.packages("ggplot2");  library(ggplot2)}
if(!require(ggforce)){install.packages("ggforce");  library(ggforce)}
if(!require(plotly)){install.packages("plotly");  library(plotly)}
if(!require(paletteer)){install.packages("paletteer");  library(paletteer)}
if(!require(ggrepel)){install.packages("ggrepel");  library(ggrepel)}
if(!require(igraph)){install.packages("igraph");  library(igraph)}
if(!require(ggraph)){install.packages("ggraph");  library(ggraph)}
if(!require(ggforce)){install.packages("ggforce");  library(ggforce)}
if(!require(shadowtext)){install.packages("shadowtext");  library(shadowtext)}
#if(!require(animation)){install.packages("animation");  library(animation)}


# MyM cnversion packages
#if(!require(mym2r)){install_github("marieyesse/mym2r");  library(mym2r)}
```

```{r data, include=FALSE}

SCEN_xlsx <-list.files(path = "../../../../../harmensytze/Projects/REINVENT/7_Reporting_Tool/outxlsx/")


SCENSdat_list <- lapply(SCEN_xlsx, function(x){ 
    dat <- read_xlsx(path=paste("../../../../../harmensytze/Projects/REINVENT/7_Reporting_Tool/outxlsx/", x, sep=""))
    dat$Scenario <- x
    dat=data.table(dat)
    })

SCENdat <- rbindlist(SCENSdat_list, fill=TRUE) %>%
    drop_na(Model) %>%
    gather(Year, value, -c(Model, Scenario, Region, Variable, Unit)) %>%
    mutate(Year=as.numeric(Year), value=as.numeric(value)) %>%
    mutate(Scenario=gsub(".xlsx", "", Scenario, fixed=T)) %>%
    drop_na(Year) %>%
        bind_rows({.} %>% filter(Region %in% c("WEU", "CEU")) %>% 
                    group_by(Model, Scenario, Variable, Unit, Year) %>% 
                    summarise(value=sum(value)) %>%
                    mutate(Region="EU")) %>%
  filter(!Region == "World") %>%
    bind_rows({.} %>% filter(!Region %in% c( "EU")) %>% 
              group_by(Model, Scenario, Variable, Unit, Year) %>% 
              summarise(value=sum(value)) %>%
              mutate(Region="World"))

SCENINDUS <- SCENdat %>%
    filter(grepl("industry", tolower(Variable), fixed=T))

``` 


Produced on: `r format(Sys.time(), '%d %B %Y - time stamp: %H:%M')`

**Known issues**:

* **Steel:** No primary production in some scenarios 
* **Steel:** Wel H-DRI, geen Electrowinning
*	**Cement:** Material Demand stijgt na 2050 weer
*	**CHemicals:** werkt nog niet / geen scenario parameterisation
*	**PPI:**  juist de Circ en DemandMan gaan heel diep negatief
*	**Food:** no change.
* Geen IMAGE data nog

## General {.tabset}


### Whole system emissions

```{r econ-emis, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=5}

ECONCO2 <- SCENdat %>%
    filter(grepl("Emissions|CO2", Variable, fixed=T)) 

ECONCO2Tot <-   ECONCO2 %>%
    #filter(grepl("emissions", tolower(Variable), fixed=T)) %>%
    filter(!grepl("Emissions|CO2|",Variable, fixed=T)) %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_line(aes(x=Year, y=value,  group=Scenario, colour=Scenario)) +
     labs(title="CO2 Emissions",
        x="Year",
        y="MtCO2/yr") +
    facet_wrap(~ Variable, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(ECONCO2Tot)

```

### Demand sector emissions

```{r dem-emis, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=10}

INDUSDEM <- SCENdat %>%
    filter(grepl("Emissions|CO2|Energy|Demand|", Variable, fixed=T)) 

INDUSDEMTot <-   INDUSDEM %>%
    #filter(grepl("emissions", tolower(Variable), fixed=T)) %>%
    #filter(!grepl("cokes", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Z", "A", "Industry", "TMI"), sep = "[|]") %>%
  filter(is.na(TMI)==T) %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_line(aes(x=Year, y=value,  group=Scenario, colour=Scenario)) +
     labs(title="CO2 Emissions",
        x="Year",
        y="MtCO2/yr") +
    facet_wrap(~ Industry, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(INDUSDEMTot)

```



## Steel {.tabset}

### CO2 Emissions

```{r steel-emis, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=5}

SCENSTEEL <- SCENdat %>%
    filter(grepl("steel", tolower(Variable), fixed=T)) 

SCENSTEELEMIS <-   SCENSTEEL %>%
    filter(grepl("emissions", tolower(Variable), fixed=T)) %>%
    filter(!grepl("cokes", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Type"), sep = "[|]") %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_line(aes(x=Year, y=value, colour=Scenario, group=Scenario)) +
     labs(title="CO2 Emissions",
        x="Year",
        y="MtCO2/yr") +
    facet_wrap(~ Type, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENSTEELEMIS)

```

### Material Demand


```{r steel-material, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7}

SCENSTEEL<- SCENdat %>%
    filter(grepl("steel", tolower(Variable), fixed=T)) 

SCENSTEELProd <-   SCENSTEEL %>%
    filter(grepl("production", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Material"), sep = "[|]") %>%
  
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(data=. %>% filter(!grepl("scrap", tolower(Material), fixed=T)), aes(x=Year, y=value, fill=Material), position="stack", colour="black") +
    geom_area(data=. %>% filter(grepl("scrap", tolower(Material), fixed=T)), aes(x=Year, y=value, fill=Material), position="stack", colour="black") +
     labs(title="Production",
        x="Year",
        y="Mt/Yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENSTEELProd)

```

### Capacity / Feedstock

```{r Steel, include=TRUE, results=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=7}

##############################################################################################################################
## Read input data
##############################################################################################################################



SCENSTEEL <- SCENdat %>%
    filter(grepl("steel", tolower(Variable), fixed=T)) 

 SCENSTEELCAP <-   SCENSTEEL %>%
    filter(grepl("capacity", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Technology"), sep = "[|]") %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Technology), position="stack", colour="black") +
   labs(title="Capacity",
        x="Year",
        y="Mt/yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENSTEELCAP)

```

### Final Energy

```{r steel-energy, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7}

SCENSTEEL <- SCENdat %>%
    filter(grepl("steel", tolower(Variable), fixed=T)) 

SCENSTEELFINE <-   SCENSTEEL %>%
    filter(grepl("final energy", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Carrier"), sep = "[|]") %>%
  filter(!is.na(Carrier)==T) %>%
  
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Carrier), position="stack", colour="black") +
     labs(title="Final Energy Use",
        x="Year",
        y="EJ/yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENSTEELFINE)

```



## Cement {.tabset}


### CO2 Emissions

```{r ce-emis, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=5}

SCENCE <- SCENdat %>%
    filter(grepl("cement", tolower(Variable), fixed=T)) 

SCENCEEMIS <-   SCENCE %>%
    filter(grepl("emissions", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Type"), sep = "[|]") %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_line(aes(x=Year, y=value, colour=Scenario, group=Scenario)) +
     labs(title="CO2 Emissions",
        x="Year",
        y="MtCO2/yr") +
    facet_wrap(~ Type, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENCEEMIS)

```

### Material Demand


```{r ce-material, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7}

SCENCE<- SCENdat %>%
    filter(grepl("non metallic", tolower(Variable), fixed=T)) 

SCENCEProd <-   SCENCE %>%
    filter(grepl("production", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Material"), sep = "[|]") %>%
  
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Material), position="stack", colour="black") +
     labs(title="Production",
        x="Year",
        y="Mt/Yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENCEProd)
```

### Capacity

```{r cement, include=TRUE, results=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7}

##############################################################################################################################
## Read input data
##############################################################################################################################



SCENCE <- SCENdat %>%
    filter(grepl("non metallic mineral", tolower(Variable), fixed=T)) 

 SCENCECAP <-   SCENCE %>%
    filter(grepl("capacity", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Technology"), sep = "[|]") %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Technology), position="stack", colour="black") +
   labs(title="Capacity",
        x="Year",
        y="Mt/yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENCECAP)

```


### Final Energy
```{r ce-energy, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7}

SCENCE <- SCENdat %>%
    filter(grepl("non metallic mineral", tolower(Variable), fixed=T)) 

SCENCEFINE <-   SCENCE %>%
    filter(grepl("final energy", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Carrier"), sep = "[|]") %>%
  filter(!is.na(Carrier)==T) %>%
  
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Carrier), position="stack", colour="black") +
     labs(title="Final Energy Use",
        x="Year",
        y="EJ/yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENCEFINE)

```


## Chemical Industry {.tabset}



### CO2 Emissions

```{r nonen-emis, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=5}

SCENCHEM <- SCENdat %>%
    filter(grepl("chemicals and petrochemicals", tolower(Variable), fixed=T)) 

SCENCHEMEMIS <-   SCENCHEM %>%
    filter(grepl("emissions", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Type"), sep = "[|]") %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_line(aes(x=Year, y=value, colour=Scenario, group=Scenario)) +
     labs(title="CO2 Emissions",
        x="Year",
        y="MtCO2/yr") +
    facet_wrap(~ Type, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENCHEMEMIS)

```

### Material Demand

This seems not mapped yet..

### Capacity / Feedstock

```{r Chemical, results=TRUE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=7}

SCENCHEM <- SCENdat %>%
    filter(grepl("chemicals and petrochemicals", tolower(Variable), fixed=T)) 

SCENCHEMCAP <-   SCENCHEM %>%
    filter(grepl("feedstock energy", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Technology"), sep = "[|]") %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Technology), position="stack", colour="black") +
     labs(title="Non-energy demand",
        x="Year",
        y="GJ/yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENCHEMCAP)
```

### Final Energy

```{r nonen-energy, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7}

SCENNONEN <- SCENdat %>%
    filter(grepl("chemicals and petrochemicals", tolower(Variable), fixed=T)) 

SCENNONENFINE <-   SCENNONEN %>%
    filter(grepl("final energy", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Carrier"), sep = "[|]") %>%
  filter(!is.na(Carrier)==T) %>%
  
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Carrier), position="stack", colour="black") +
     labs(title="Final Energy Use",
        x="Year",
        y="EJ/yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENNONENFINE)

```


HVC emissions variable seems not reported

## Pulp & Paper Industry {.tabset}

### CO2 Emissions

```{r ppi-emis, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=5}

SCENPPI <- SCENdat %>%
    filter(grepl("pulp and paper", tolower(Variable), fixed=T)) 

SCENPPIEMIS <-   SCENPPI %>%
    filter(grepl("emissions", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Type"), sep = "[|]") %>%
  
    filter(Region=="World" ) %>%
    ggplot()+
    geom_line(aes(x=Year, y=value, colour=Scenario, group=Scenario)) +
     labs(title="CO2 Emissions",
        x="Year",
        y="MtCO2/yr") +
    facet_wrap(~ Type, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENPPIEMIS)

```

### Material Demand

Data not working / erroneously mapped


```{r ppi-material, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7}

SCENPPI <- SCENdat %>%
    filter(grepl("pulp and paper", tolower(Variable), fixed=T))

SCENPPIProd <-   SCENPPI %>%
    filter(grepl("production", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Food"), sep = "[|]") %>%
  filter(!Food=="Total") %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Food), position="stack", colour="black") +
     labs(title="Production",
        x="Year",
        y="Mt/Yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENPPIProd)
```


### Capacity / Feedstock

```{r ppi, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=11, fig.height=7}

SCENPPI <- SCENdat %>%
    filter(grepl("pulp and paper", tolower(Variable), fixed=T)) 

SCENPPICAP <-   SCENPPI %>%
    filter(grepl("capacity", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Type", "Technology", "Carrier"), sep = "[|]") %>%
  mutate(Technology=paste(Technology, Carrier)) %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Technology), position="stack", colour="black") +
     labs(title="Energy demand",
        x="Year",
        y="MWth") +
    facet_grid(Type~ Scenario) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENPPICAP)
```

### Final Energy

```{r ppi-energy, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7}

SCENPPI <- SCENdat %>%
    filter(grepl("pulp and paper", tolower(Variable), fixed=T)) 

SCENPPIFINE <-   SCENPPI %>%
    filter(grepl("final energy", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Carrier"), sep = "[|]") %>%
  filter(!is.na(Carrier)==T) %>%
  
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Carrier), position="stack", colour="black") +
     labs(title="Final Energy Use",
        x="Year",
        y="EJ/yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENPPIFINE)

```




## Food Industry {.tabset}

### CO2 Emissions

```{r food-emis, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=5}

SCENFOOD <- SCENdat %>%
    filter(grepl("food", tolower(Variable), fixed=T)) 

SCENFOODEMIS <-   SCENFOOD %>%
    filter(grepl("emissions", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Type"), sep = "[|]") %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_line(aes(x=Year, y=value, colour=Scenario, group=Scenario)) +
     labs(title="CO2 Emissions",
        x="Year",
        y="MtCO2/yr") +
    facet_wrap(~ Type, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENFOODEMIS)

```

### Material Demand

```{r food-material, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7}

SCENFood <- SCENdat %>%
    filter(grepl("food", tolower(Variable), fixed=T)) 

SCENFoodProd <-   SCENFood %>%
    filter(grepl("production", tolower(Variable), fixed=T)) %>%
    filter(grepl("minor", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Z", "Food"), sep = "[|]") %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Food), position="stack", colour="black") +
     labs(title="Production",
        x="Year",
        y="Mt/Yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENFoodProd)
```


### Capacity / Feedstock

```{r food, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=11, fig.height=7}

SCENFood <- SCENdat %>%
    filter(grepl("food", tolower(Variable), fixed=T)) 

SCENFoodCAP <-   SCENFood %>%
    filter(grepl("capacity", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Z", "Type", "Technology", "Carrier"), sep = "[|]") %>%
  mutate(Technology=paste(Technology, Carrier)) %>%
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Technology), position="stack", colour="black") +
     labs(title="Energy demand",
        x="Year",
        y="MWth") +
    facet_grid(Type~ Scenario) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENFoodCAP)
```

### Final Energy

```{r food-energy, echo=FALSE, results=TRUE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7}

SCENFOOD <- SCENdat %>%
    filter(grepl("food", tolower(Variable), fixed=T)) 

SCENFOODFINE <-   SCENFOOD %>%
    filter(grepl("final energy", tolower(Variable), fixed=T)) %>%
   filter(!grepl("electricity|", tolower(Variable), fixed=T)) %>%
  filter(!grepl("heat|", tolower(Variable), fixed=T)) %>%
    separate(Variable, c("X", "Y", "Industry", "Carrier"), sep = "[|]") %>%
  filter(!is.na(Carrier)==T) %>%
  
    filter(Region=="World" ) %>%
    ggplot()+
    geom_area(aes(x=Year, y=value, fill=Carrier), position="stack", colour="black") +
     labs(title="Final Energy Use",
        x="Year",
        y="EJ/yr") +
    facet_wrap(~ Scenario, ncol=2) +
         theme(axis.text.x = element_text(angle=45, hjust=1),
               text = element_text(size=14))

 ggplotly(SCENFOODFINE)

```


